A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-26 main.tex
Writing properties.

\begin{theorem}[Substituition Lemma for Variables of Terms, Types or Kinds and Their Equivalence]
	\begin{flalign*}
		\text{If\ } \G,z:\xi @B \V M:\tau @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P] @A.&\\
		\text{If\ } \G,z:\xi @B \V \tau::K @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P] @A.&\\
		\text{If\ } \G,z:\xi @B \V K\iskind @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V K[z \mapsto P] \iskind  @A.&\\
		\text{If\ } \G,z:\xi @B \V M\E N : \tau @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P] @A.&\\
		\text{If\ } \G,z:\xi @B \V \tau\E \sigma : K @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P] @A.&\\
		\text{If\ } \G,z:\xi @B \V K\E J @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P] @A.&
	\end{flalign*}
\end{theorem}

\begin{theorem}[Stage Substituition Lemma for Variables of Terms, Types or Kinds and Their Equivalence]
	\begin{flalign*}
		\text{If\ } \G \V M:\tau @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V \tau::K @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V K\iskind @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V M\E N : \tau @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]\E N[\beta \mapsto \epsilon] : \tau[\beta \mapsto \epsilon]  @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V \tau\E \sigma : K @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V K\E J @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&
	\end{flalign*}
\end{theorem}

>>>>

In this section, we prove some properties of \LMD: subject reduction, strong normalization, confluence,
unique decomposition of evaluation contexts, and progress.

Substitution lemma for \LMD\ is little more complicated than ordinary one 
because there are six types of judgement and two types of substitution in \LMD.

\begin{theorem}[Substituition Lemma]
	\begin{flalign*}
		\text{If\ } \G,z:\xi @B \V M:\tau @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P] @A.&\\
		\text{If\ } \G,z:\xi @B \V \tau::K @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P] @A.&\\
		\text{If\ } \G,z:\xi @B \V K\iskind @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V K[z \mapsto P] \iskind  @A.&\\
		\text{If\ } \G,z:\xi @B \V M\E N : \tau @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P] @A.&\\
		\text{If\ } \G,z:\xi @B \V \tau\E \sigma : K @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P] @A.&\\
		\text{If\ } \G,z:\xi @B \V K\E J @A \text{\ and\ } \G\V P:\xi @B
		&\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P] @A.&
	\end{flalign*}
\end{theorem}

\begin{proof}
	Straightforward induction on derivations.
\end{proof}

\begin{theorem}[Stage Substituition Lemma]
	\begin{flalign*}
		\text{If\ } \G \V M:\tau @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V \tau::K @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V K\iskind @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V M\E N : \tau @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]\E N[\beta \mapsto \epsilon] : \tau[\beta \mapsto \epsilon]  @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V \tau\E \sigma : K @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
		\text{If\ } \G \V K\E J @A
		&\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&
	\end{flalign*}
\end{theorem}

\begin{proof}
	Straightforward induction on derivations.
\end{proof}
